\textls[-0]{\thetitle}

### 2022-11-11 casestudies.tex
resolve comments
tweaks

The current plugin implementation does not yet support
mutually inductive types or mutual induction, which are
useful for modeling languages much more complex than STLCs.
However,
we believe generalizing our design to mutually inductive types does
not pose theoretical challenges.

@@

Our second case study is a mechanization of abstract interpreters
for simple imperative languages.
In addition to the metatheories, this case study produces abstract
interpreters that are directly ready for program extraction in Coq.

@@

\begin{wrapfigure}[13]{r}{0.13\textwidth}
\includegraphics[scale=.68]{graphics/ai-casestudy.pdf}
\end{wrapfigure}

@@

In addition to the two case studies above, we also use extensible
inductive types for modeling extensible context-free grammars and derive
decision procedures for them.

>>>>

The current plugin implementation does not yet support
mutually inductive types or mutual induction, which are
useful for modeling languages much more complex than STLCs.
However,
we believe accommodating mutually inductive types does
not pose theoretical challenges.

@@

Our second case study is a mechanization of abstract interpreters
for simple imperative languages.
In addition to the metatheories, this case study produces abstract
interpreters that are directly ready for program extraction.

@@

\begin{wrapfigure}[13]{r}{0.138\textwidth}
\includegraphics[scale=.68]{graphics/ai-casestudy.pdf}
\end{wrapfigure}

@@

In addition to the two case studies above, we also use extensible
inductive types for modeling extensible context-free grammars and derive
decision procedures for them.
%\EDJ{I will suggest change to ``and derive decision procedures for them (based on naive parsing by enumeration)''.}
